The Concurrent Calculi Formalisation Benchmark

### 2024-02-12 short-paper/short-paper.tex
Shorten and improve introduction.

% - Introduction
%   - POPLMark accelerated progress in mechanisation tools for PL
%     - POPLMark Reloaded tried to do the same for logical relations
%     - But they were deliberately limited in scope to not include process calculi
%   - We propose a new collection of benchmark problems for process calculi
%     - Why not concurrency in general? (after this point, only mention process calculi)
%     - Why is there a problem with process calculus mechanisations?
%     - Our experience says there is, and we will cite other experiences below
%   - We have noticed three key issues
%     - They are not covered by POPLMark
%     - Techniques are less settled than for binders
%     - Others also mention them as problems: cite and explain references briefly for each challenge topic
%   - Our goals are to determine the state of the art, develop best practices and tutorials, and identify improvements to proof assistant technology that would materially help the situation
\section{Introduction}
The POPLMark challenge~\cite{POPLMark} accelerated the development of proof assistants, libraries, and best practices for programming language mechanisation by establishing a common ground for systematically evaluating mechanisation techniques.
In doing so, it spearheaded a shift in the programming language research community towards publications that include mechanised proofs.
POPLMark Reloaded~\cite{POPLMarkReloaded} proposed a similar program for proofs involving logical relations.
These challenges, and therefore the developments they spurred, were deliberately limited in scope, but their authors noted the need for future benchmarks to tackle such areas as coinduction and linear environments.

@@

Our benchmark problems (explained in detail in \cref{app:challenges}) are designed to focus on three key aspects which typically cause difficulties when mechanising concurrency theory: \emph{linearity}, \emph{scope extrusion}, and \emph{coinductive reasoning}.
The mechanisation of novel research results often requires addressing more than just one of these aspects at once; we see the combination of techniques as a next step beyond the scope of this challenge, as discussed further in \Cref{sec:going-beyond}.
Our benchmark challenges are based on process calculi, as these provide a simple but realistic exhibit of the issues typically encountered when mechanising the three key aspects.
These three aspects are certainly not the only causes of difficulties, but they are fundamental to concurrency theory, and emerge in most mechanisations, as we will see presently while discussing the issues presented by them.

>>>>

% - Introduction
%   - POPLMark accelerated progress in mechanisation tools for PL
%     - POPLMark Reloaded tried to do the same for logical relations
%     - But they were deliberately limited in scope to not include process calculi
%   - We propose a new collection of benchmark problems for process calculi
%     - Why not concurrency in general? (after this point, only mention process calculi)
%     - Why is there a problem with process calculus mechanisations?
%     - Our experience says there is, and we will cite other experiences below
%   - We have noticed three key issues
%     - They are not covered by POPLMark
%     - Techniques are less settled than for binders
%     - Others also mention them as problems: cite and explain references briefly for each challenge topic
%   - Our goals are to determine the state of the art, develop best practices and tutorials, and identify improvements to proof assistant technology that would materially help the situation
\section{Introduction}
The POPLMark challenge~\cite{POPLMark} accelerated the development of proof assistants, libraries, and best practices for programming language mechanisation by establishing a common ground for systematically evaluating mechanisation techniques.
In doing so, it spearheaded a shift in the programming language research community towards publications that include mechanised proofs.
POPLMark Reloaded~\cite{POPLMarkReloaded} proposed a similar program for proofs involving logical relations.
These challenges, and the developments they spurred, were limited in scope, but their authors noted the need to tackle topics such as coinduction and linearity in the future.

@@

Our benchmark problems (explained in detail in \cref{app:challenges}) focus on three key aspects which often cause difficulties when mechanising concurrency theory: \emph{linearity}, \emph{scope extrusion}, and \emph{coinductive reasoning}.
Mechanisations must often address several of these aspects, but we see the combination of techniques as a next step beyond the scope of this challenge, as discussed further in \Cref{sec:going-beyond}.
Our benchmark challenges are based on process calculi, as these provide a simple but realistic exhibit of typical issues encountered in mechanisation work.
The three aspects are certainly not the only causes of difficulties, but as we will discuss presently, they emerge in most mechanisations of concurrency theory.
